Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-05-22 paper_jasa.tex
made suggested *** changes

@@

@@

\begin{figure}[htp]
%\begin{figurehere}
   \centering
       \includegraphics[width=0.95\textwidth]{test_category.pdf}
       \caption{Lineup plot ($m=20$) using side-by-side boxplots for testing $H_0: \beta_k=0$. One of these plots is the plot of the actual data, and the remaining are null plots, produced by simulating data from a null model that assumes $H_0$ is true. Which plot is the most different from the others, in the sense that there is the the largest shift or location difference between the boxplots? *** Make the legend text use a subscript}
       \label{fig:test_category}
\end{figure}
%\end{figurehere}

@@

\begin{table*}[hbtp]
\caption{Comparison of visual inference with existing inference technique. *** The plot for the traditional test is wrong, for two sided, p-value is area to the right and left of $|T(y|$.}
\centering 
\begin{tabular}{llll} 
\hline
  & Traditional Inference &  Lineup Protocol \\ %[0.5ex] % inserts table %heading 
\hline
  Hypothesis & $H_0: \beta=0$ vs $H_1: \beta \ne 0$& $H_0: \beta=0$ vs $H_1: \beta \ne 0$\\
 & \begin{minipage}[h]{2.5cm} \begin{center} \scalebox{0.2}{\includegraphics{down_arrow.pdf}} \end{center} \end{minipage} & \begin{minipage}[h]{2.5cm} \begin{center} \scalebox{0.2}{\includegraphics{down_arrow.pdf}} \end{center} \end{minipage} \\

@@

 Sampling Distribution & $f_{T(y)}(t); $\begin{minipage}[h]{2.5cm} \begin{center} \scalebox{0.55}{\includegraphics{stat_mathematical_test.pdf}} \end{center} \end{minipage} & $f_{T(y)}(t); $ \begin{minipage}[h]{2.5cm} \begin{center} \scalebox{0.19}{\includegraphics{test_category.pdf}} \end{center} \end{minipage} \\
 & \begin{minipage}[h]{2.5cm} \begin{center} \scalebox{0.2}{\includegraphics{down_arrow.pdf}} \end{center} \end{minipage} & \begin{minipage}[h]{2.5cm} \begin{center} \scalebox{0.2}{\includegraphics{down_arrow.pdf}} \end{center} \end{minipage} \\
 Reject $H_0$ if & observed $T$ is extreme & observed plot is identifiable \\
\hline 
\end{tabular}
\label{tbl:compare}
\end{table*}

>>>>

% \usepackage{pifont} % this package is used to print check mark \checkmark

@@

%\checkmark

@@

\begin{figure}[htp]
%\begin{figurehere}
   \centering
       \includegraphics[width=0.95\textwidth]{test_category.pdf}
       \caption{Lineup plot ($m=20$) using side-by-side boxplots for testing $H_0: \beta_k=0$. One of these plots is the plot of the actual data, and the remaining are null plots, produced by simulating data from a null model that assumes $H_0$ is true. Which plot is the most different from the others, in the sense that there is the the largest shift or location difference between the boxplots? *** Make the legend text use a subscript (MM: is it ok now?)}
       \label{fig:test_category}
\end{figure}
%\end{figurehere}

@@

\begin{table*}[hbtp]
\caption{Comparison of visual inference with existing inference technique. *** The plot for the traditional test is wrong, for two sided, p-value is area to the right and left of $|T(y|$. (MM: the vertical bar is showing the observed $T$ location not p-value.) }
\centering 
\begin{tabular}{llll} 
\hline
  & Traditional Inference &  Lineup Protocol \\ %[0.5ex] % inserts table %heading 
\hline
  Hypothesis & $H_0: \beta=0$ vs $H_1: \beta \ne 0$& $H_0: \beta=0$ vs $H_1: \beta \ne 0$\\
 & \begin{minipage}[h]{2.5cm} \begin{center} \scalebox{0.2}{\includegraphics{down_arrow.pdf}} \end{center} \end{minipage} & \begin{minipage}[h]{2.5cm} \begin{center} \scalebox{0.2}{\includegraphics{down_arrow.pdf}} \end{center} \end{minipage} \\

@@

 Sampling Distribution & $f_{T(y)}(t); $\begin{minipage}[h]{2.5cm} \begin{center} \scalebox{0.55}{\includegraphics{stat_mathematical_test.pdf}} \end{center} \end{minipage} & $f_{T(y)}(t); $ \begin{minipage}[h]{2.5cm} \begin{center} \scalebox{0.32}{\includegraphics{test_category_small.pdf}} \end{center} \end{minipage} \\
 & \begin{minipage}[h]{2.5cm} \begin{center} \scalebox{0.2}{\includegraphics{down_arrow.pdf}} \end{center} \end{minipage} & \begin{minipage}[h]{2.5cm} \begin{center} \scalebox{0.2}{\includegraphics{down_arrow.pdf}} \end{center} \end{minipage} \\
 Reject $H_0$ if & observed $T$ is extreme & observed plot is identifiable \\
\hline 
\end{tabular}
\label{tbl:compare}
\end{table*}
